### 2019-10-30 docs/ICTT2019/RMethod_ictt26.tex
revert to a proper element tree

%
% FIRST AUTHORS
%
\setlength{\baselineskip}{12pt}
\textbf{Daniele Tomatis}\\
DEN, Service d'{\'e}tudes des r\'eacteurs et de math\'ematiques appliqu\'ees (SERMA),\\
CEA, Universit\'e Paris-Saclay, F-91191 Gif-sur-Yvette, France\\
daniele.tomatis@cea.fr\\
\vspace{0.25in}
\textbf{Roy Gross and Erez Gilad}\\
Unit of Nuclear Engineering\\
Ben-Gurion University of the Negev, Israel\\
roygros@post.bgu.ac.il, gilade@bgu.ac.il\\
\end{center}

>>>>

%
% FIRST AUTHORS
%
\setlength{\baselineskip}{12pt}
\textbf{Daniele Tomatis}\\
DEN, Service d'{\'e}tudes des r\'eacteurs et de math\'ematiques appliqu\'ees (SERMA),\\
CEA, Universit\'e Paris-Saclay, F-91191 Gif-sur-Yvette, France\\
daniele.tomatis@cea.fr\\
\vspace{0.25in}
\textbf{Roy Gross and Erez Gilad}\\
The Unit of Nuclear Engineering\\
Ben-Gurion University of the Negev, Israel\\
roygros@post.bgu.ac.il, gilade@bgu.ac.il\\
\end{center}
